Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-05-03 paper/paper1/ms.tex
add some software references
latex formatting tiny

\subsection{Pre-processing with \texttt{muler}}

@@

\begin{acknowledgements}
    This research has made use of NASA’s Astrophysics Data System.
\end{acknowledgements}

\facilities{Smith (IGRINS), Gaia, ASAS}

\software{  pandas \citep{mckinney10},
    emcee \citep{foreman13},
    matplotlib \citep{hunter07},
    numpy \citep{2020NumPy-Array},
    scipy \citep{2020SciPy-NMeth},
    ipython \citep{perez07},
    seaborn \citep{waskom14}}

>>>>

\subsection{Pre-processing with \texttt{muler} }

@@

\begin{acknowledgements}
    This research has made use of NASA's Astrophysics Data System.
\end{acknowledgements}

\facilities{HET (HPF), TESS, ASAS}

\software{  \texttt{pandas} \citep{mckinney10},
    \texttt{emcee} \citep{foreman13},
    \texttt{matplotlib} \citep{hunter07},
    \texttt{numpy} \citep{2020NumPy-Array},
    \texttt{scipy} \citep{2020SciPy-NMeth},
    \texttt{ipython} \citep{perez07},
    \texttt{seaborn} \citep{waskom14},
    \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A},
    \texttt{muler} (Gully-Santiago et al., submitted),
    \texttt{telfit} \citep{2014AJ....148...53G},
    \texttt{jupyter} \citep{Kluyver2016jupyter}}
